Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-03-01 manuscripts/reply/reply-abstract.tex
Reformating reply ms for Evolution.
Also moving the abstract and acknowledgments to separate files, and
resizing the sampling error figure to fit within the margins.

%&<latex>
\documentclass[letterpaper,12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\usepackage[round]{natbib}
\input{../utils/macros.tex}

\title{Implications of uniformly distributed, empirically informed priors for
phylogeographical model selection: A reply to Hickerson et al.}

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}\thanks{Current address: Department of Biology, University of Washington, Seattle, Washington 98195}}
\author[2]{Charles W.\ Linkem}
\author[3]{Jeet Sukumaran}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence, Kansas 66045}
\affil[2]{Department of Biology, University of Washington, Seattle, Washington 98195}
\affil[3]{Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan 48109}

% \date{\today}
\date{\parbox{\linewidth}{\centering%
    \today\endgraf\bigskip
    \textbf{Running head}: Approximate Bayesian model choice}}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \doublespacing
% \raggedright
% \setlength{\parindent}{0.5in}
% \begin{linenumbers}

\maketitle

\begin{abstract}
    Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citet{Huang2011} introduced an approximate Bayesian approach (implemented
    in the software \msb) which can be used to estimate the probabilities of
    models in which multiple sets of taxa diverge at the same time. 
    % This method  does not require a common set of character data that links all
    % of the taxa under investigation, but does require the relative mutation
    % rates among the taxa and loci to be assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the prior and
    that the inference method had low power to detect variation in divergences
    times.
    These results were not surprising, in light of a rich statistical literature
    showing that the marginal likelihood of a model is sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times, leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically
    informed uniform priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an empirical
    Bayesian stance for this model-choice problem, because it can mislead model
    posterior probabilities, which are inherently measures of belief in the
    models after prior knowledge is updated by the data.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes} 
\end{abstract}

\newpage

\input{reply-main.tex}

\section{Acknowledgments}
We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, and Adam Leach\'{e} for
insightful comments that greatly improved this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

\bibliographystyle{../bib/evolution.bst}
\bibliography{../bib/references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\renewcommand\listfigurename{Figure Captions}
\cftsetindents{fig}{0cm}{2.2cm}
\renewcommand\cftdotsep{\cftnodots}
\setlength\cftbeforefigskip{10pt}
\cftpagenumbersoff{fig}
\listoffigures

% \end{linenumbers}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\input{reply-tables.tex}

\clearpage

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\input{reply-figures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}

\singlespacing

\section*{Supporting Information}
% PUT MAIN TEXT CITATION HERE
\hangindent=1cm
Oaks, J.~R., C.~W.\ Linkem, and J.~Sukumaran. \msTitle

% \doublespacing
\input{reply-si-main.tex}

\newpage
\singlespacing

\input{reply-si-figures.tex}

\end{document}

>>>>

Biogeographers frequently seek to explain population and species
differentiation on geographical phenomena.
Establishing that a set of population splitting events occurred
at the same time can be a potentially persuasive argument that a set of taxa
were affected by the same geographic events.
Unfortunately, estimating divergence times precisely when one lacks
precise information about the rate of molecular evolution is a notoriously
difficult problem in evolutionary biology.
\citet{Huang2011} introduced an approximate Bayesian approach (implemented
in the software \msb) which can be used to estimate the probabilities of
models in which multiple sets of taxa diverge at the same time. 
% This method  does not require a common set of character data that links all
% of the taxa under investigation, but does require the relative mutation
% rates among the taxa and loci to be assumed \emph{a priori}.
Recently, \citet{Oaks2012} used this model-choice framework to 
study 22 pairs of vertebrate lineages which are distributed across
the Philippines; they also studied the behavior of the \msb approach
using computer simulations.
\citet{Oaks2012} found that the model was very sensitive to the prior and
that the inference method had low power to detect variation in divergences
times.
These results were not surprising, in light of a rich statistical literature
showing that the marginal likelihood of a model is sensitive to the
use of vague priors.
Because this sensitivity to prior assumptions affects the crucial insights 
that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
that users of the approach should carefully assess the robustness of their 
conclusions to different priors.
According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
was due to excessively broad priors on divergence times, leading to 
inadequate numbers of simulation replicates.
They proposed a new model-averaging approach that uses narrow, empirically
informed uniform priors.
Here we demonstrate that the approach of \citet{Hickerson2013} is
dangerous in the sense that the empirically-derived priors often
exclude from consideration the true values of the models' parameters.
On a more fundamental level, we question the value of adopting an empirical
Bayesian stance for this model-choice problem, because it can mislead model
posterior probabilities, which are inherently measures of belief in the
models after prior knowledge is updated by the data.
The robust Bayesian approach of conducting analyses under a variety
of priors can reveal prior sensitivity and communicate which assumptions
underlie model inference.
Furthermore, simulations provide insight into the temporal resolution of
the method, which in turn helps guide interpretation of results.

### 2014-03-01 manuscripts/reply/reply-acknowledgments.tex
Reformating reply ms for Evolution.
Also moving the abstract and acknowledgments to separate files, and
resizing the sampling error figure to fit within the margins.

%&<latex>
\documentclass[letterpaper,12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\usepackage[round]{natbib}
\input{../utils/macros.tex}

\title{Implications of uniformly distributed, empirically informed priors for
phylogeographical model selection: A reply to Hickerson et al.}

\author[1]{Jamie R.\ Oaks\thanks{Corresponding author: \href{mailto:joaks1@gmail.com}{\tt joaks1@gmail.com}}\thanks{Current address: Department of Biology, University of Washington, Seattle, Washington 98195}}
\author[2]{Charles W.\ Linkem}
\author[3]{Jeet Sukumaran}
\affil[1]{Department of Ecology and Evolutionary Biology, University of Kansas, Lawrence, Kansas 66045}
\affil[2]{Department of Biology, University of Washington, Seattle, Washington 98195}
\affil[3]{Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan 48109}

% \date{\today}
\date{\parbox{\linewidth}{\centering%
    \today\endgraf\bigskip
    \textbf{Running head}: Approximate Bayesian model choice}}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \doublespacing
% \raggedright
% \setlength{\parindent}{0.5in}
% \begin{linenumbers}

\maketitle

\begin{abstract}
    Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citet{Huang2011} introduced an approximate Bayesian approach (implemented
    in the software \msb) which can be used to estimate the probabilities of
    models in which multiple sets of taxa diverge at the same time. 
    % This method  does not require a common set of character data that links all
    % of the taxa under investigation, but does require the relative mutation
    % rates among the taxa and loci to be assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the prior and
    that the inference method had low power to detect variation in divergences
    times.
    These results were not surprising, in light of a rich statistical literature
    showing that the marginal likelihood of a model is sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times, leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically
    informed uniform priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an empirical
    Bayesian stance for this model-choice problem, because it can mislead model
    posterior probabilities, which are inherently measures of belief in the
    models after prior knowledge is updated by the data.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes} 
\end{abstract}

\newpage

\input{reply-main.tex}

\section{Acknowledgments}
We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, and Adam Leach\'{e} for
insightful comments that greatly improved this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

\bibliographystyle{../bib/evolution.bst}
\bibliography{../bib/references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\renewcommand\listfigurename{Figure Captions}
\cftsetindents{fig}{0cm}{2.2cm}
\renewcommand\cftdotsep{\cftnodots}
\setlength\cftbeforefigskip{10pt}
\cftpagenumbersoff{fig}
\listoffigures

% \end{linenumbers}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\input{reply-tables.tex}

\clearpage

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\input{reply-figures.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}

\singlespacing

\section*{Supporting Information}
% PUT MAIN TEXT CITATION HERE
\hangindent=1cm
Oaks, J.~R., C.~W.\ Linkem, and J.~Sukumaran. \msTitle

% \doublespacing
\input{reply-si-main.tex}

\newpage
\singlespacing

\input{reply-si-figures.tex}

\end{document}

>>>>

We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, and Adam Leach\'{e} for
insightful comments that greatly improved this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

### 2014-03-01 manuscripts/reply/reply-figures.tex
A few edits to reply ms.
Reformating reply ms for Evolution.
Also moving the abstract and acknowledgments to separate files, and
resizing the sampling error figure to fit within the margins.

%% Sampling error
\mFigure{../../response-redux/results/sampling-error/pymsbayes-results/omega_over_sampling.pdf}{
    Traces of the estimated lower and upper limits of the 95\% highest posterior density (HPD)
    interval of \vmratio{} (the dispersion index of divergence times) as 100 million prior
    samples are accumulated. Each pair of points is based on 1000 posterior samples retained
    from the prior. Both (A) unadjusted and (b) GLM-regression-adjusted estimates are shown.
    Prior settings were $\divt{} \sim U(0,10)$, $\meanDescendantTheta{} \sim U(0.0005, 0.04)$,
    and $\ancestralTheta{} \sim U(0.0005, 0.02)$.
}{figSamplingError}

>>>>

%% Sampling error
\widthFigure{0.9}{../../response-redux/results/sampling-error/pymsbayes-results/omega_over_sampling.pdf}{listformat=figList}{
    Traces of the estimated lower and upper limits of the 95\% highest posterior density (HPD)
    interval of \vmratio{} (the dispersion index of divergence times) as 100 million prior
    samples are accumulated. Each pair of points is based on 1000 posterior samples retained
    from the prior. Both (A) unadjusted and (B) GLM-regression-adjusted estimates are shown.
    The data analyzed were the 22 pairs of Philippine taxa from \citet{Oaks2012}.
    Prior settings were $\divt{} \sim U(0,10)$, $\meanDescendantTheta{} \sim U(0.0005, 0.04)$,
    and $\ancestralTheta{} \sim U(0.0005, 0.02)$.
}{figSamplingError}
\clearpage

### 2014-03-01 manuscripts/reply/reply.tex
Moving `bibliographystyle` call in manuscripts.
Moving from preamble to main tex documents for each of the manuscripts.
Moving use of natbib to reply ms only.
Reformating reply ms for Evolution.
Also moving the abstract and acknowledgments to separate files, and
resizing the sampling error figure to fit within the margins.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/macros.tex}

@@

% \date{\today}
\date{\parbox{\linewidth}{\centering%
    \today\endgraf\bigskip
    \textbf{Running head}: Approximate Bayesian model choice}}

@@

\begin{document}
% \doublespacing
% \raggedright
% \setlength{\parindent}{0.5in}
% \begin{linenumbers}

@@

\begin{abstract}
    Biogeographers frequently seek to explain population and species
    differentiation on geographical phenomena.
    Establishing that a set of population splitting events occurred
    at the same time can be a potentially persuasive argument that a set of taxa
    were affected by the same geographic events.
    Unfortunately, estimating divergence times precisely when one lacks
    precise information about the rate of molecular evolution is a notoriously
    difficult problem in evolutionary biology.
    \citet{Huang2011} introduced an approximate Bayesian approach (implemented
    in the software \msb) which can be used to estimate the probabilities of
    models in which multiple sets of taxa diverge at the same time. 
    % This method  does not require a common set of character data that links all
    % of the taxa under investigation, but does require the relative mutation
    % rates among the taxa and loci to be assumed \emph{a priori}.
    Recently, \citet{Oaks2012} used this model-choice framework to 
    study 22 pairs of vertebrate lineages which are distributed across
    the Philippines; they also studied the behavior of the \msb approach
    using computer simulations.
    \citet{Oaks2012} found that the model was very sensitive to the prior and
    that the inference method had low power to detect variation in divergences
    times.
    These results were not surprising, in light of a rich statistical literature
    showing that the marginal likelihood of a model is sensitive to the
    use of vague priors.
    Because this sensitivity to prior assumptions affects the crucial insights 
    that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
    that users of the approach should carefully assess the robustness of their 
    conclusions to different priors.
    According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
    was due to excessively broad priors on divergence times, leading to 
    inadequate numbers of simulation replicates.
    They proposed a new model-averaging approach that uses narrow, empirically
    informed uniform priors.
    Here we demonstrate that the approach of \citet{Hickerson2013} is
    dangerous in the sense that the empirically-derived priors often
    exclude from consideration the true values of the models' parameters.
    On a more fundamental level, we question the value of adopting an empirical
    Bayesian stance for this model-choice problem, because it can mislead model
    posterior probabilities, which are inherently measures of belief in the
    models after prior knowledge is updated by the data.
    The robust Bayesian approach of conducting analyses under a variety
    of priors can reveal prior sensitivity and communicate which assumptions
    underlie model inference.
    Furthermore, simulations provide insight into the temporal resolution of
    the method, which in turn helps guide interpretation of results.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes} 
\end{abstract}

@@

\section{Acknowledgments}
We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, and Adam Leach\'{e} for
insightful comments that greatly improved this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

\bibliography{../bib/references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

@@

% \end{linenumbers}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\usepackage[round]{natbib}
\input{../utils/macros.tex}

\newcommand{\keywords}{Approximate Bayesian computation; Bayesian model choice;
empirical Bayes; phylogeography; biogeography\xspace}

@@

% \date{\today}
\date{\parbox{\linewidth}{\centering%
    \today\endgraf\bigskip
    \textbf{Running head}: Approximate Bayesian model choice\endgraf\bigskip
    \textbf{Key words}: \keywords\endgraf\bigskip
    \textbf{Counts}: 7219 words, 7 figures, 1 table, 7 supporting figures\endgraf\bigskip
    \textbf{Archival location}: \href{https://github.com/joaks1/msbayes-experiments}{\url{https://github.com/joaks1/msbayes-experiments}}}}

@@

\begin{document}

@@

\newpage
\doublespacing
\raggedright
% \setlength{\parindent}{0.5in}
\begin{linenumbers}

\begin{abstract}
    \input{reply-abstract.tex}

    % \vspace{12pt}
    % \noindent\textbf{KEY WORDS: \keywords} 
\end{abstract}

@@

\section{Acknowledgments}
\input{reply-acknowledgments.tex}

\bibliographystyle{../bib/evolution.bst}
\bibliography{../bib/references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
% \singlespacing

@@

\end{linenumbers}
